The role of cross-linguistic lexical similarity on bilingual word acquisition

### 2020-07-03 Manuscript/trajectories_manuscript.Rmd
Final revision of poster, second attempt on productive data

library(magrittr)
library(tidyverse)
library(dplyr)
library(forcats)
library(stringr)
library(readxl)
library(lubridate)
library(janitor)

library(ggridges)
library(patchwork)
library(gt)

@@

# set params
bins <- c("14-16", "16-18", "18-20", "20-22", "22-24", "24-26", "26-28", "28-30", "30-32", "32-34", "34-36")

# import data 
dat_studies <- fread(here("Data", "00_studies.csv")) %>% distinct(q_version, language, q_items)
dat_items <- read_xlsx(here("Data", "01_pool.xlsx")) %>%
  group_by() %>%
  drop_na(language) %>%
  mutate_at(vars(A, B, C, D, cognate_rater1, include, frequency), as.numeric) %>%
  mutate_at(vars(A, B, C, D, cognate_rater1, include), as.logical)
dat_participants <- list.files(here("Data", "Logs"), pattern = "logs", full.names = TRUE) %>%
  last() %>%
  fread(na.strings = "") %>%
  filter(age_bin %in% bins,
         completed,
         lp == "Bilingual")
dat_raw <- fread(here("Data", "02_merged.csv"), na.strings = "") %>%
  filter(lp %in% c("Bilingual"),
         age_bin %in% bins) %>%
  as_tibble() %>%
  mutate_at(vars(date_birth, time_stamp), as_date)

dat_wordbank <- fread(here("Data", "05_wordbank.csv"))
dat_wordbank_priors <- fread(here("Data", "05_priors-wordbank.csv"))

@@

## Hypothesis 1

@@

>>>>

library(magrittr)
library(tidyverse)
library(readxl)
library(lubridate)
library(janitor)

library(broom)
library(ggridges)
library(patchwork)
library(gt)

@@

# set params
bins <- c("12-14", "14-16", "16-18", "18-20", "20-22", "22-24", "24-26", "26-28", "28-30", "30-32", "32-34")

# import data 
dat_studies <- fread(here("Data", "00_studies.csv")) %>% distinct(q_version, language, q_items)
dat_items <- read_xlsx(here("Data", "01_pool.xlsx")) %>%
  group_by() %>%
  drop_na(language) %>%
  mutate_at(vars(A, B, C, D, cognate_rater1, include, frequency), as.numeric) %>%
  mutate_at(vars(A, B, C, D, cognate_rater1, include), as.logical)
dat_participants <- list.files(here("Data", "Logs"), pattern = "logs", full.names = TRUE) %>%
  last() %>%
  fread(na.strings = "") %>%
  filter(age_bin %in% bins,
         completed,
         lp == "Bilingual")
dat_raw <- fread(here("Data", "02_merged.csv"), na.strings = "") %>%
  filter(lp %in% c("Bilingual"),
         age_bin %in% bins) %>%
  as_tibble() %>%
  mutate_at(vars(date_birth, time_stamp), as_date)
dat_wordbank <- fread(here("Data", "05_wordbank.csv"))
dat_wordbank_priors <- fread(here("Data", "05_priors-wordbank.csv"))

# import results
comp_fit1 <- readRDS(here("Results", "comp_fit1.rds"))
comp_selection <- readRDS(here("Results", "comp_selection.rds"))

@@

## Hypothesis 1: Are cognates acquired ealier?

@@

Table \@ref(tab:resultscomp) shows the outcomes of the model.

```{r resultscomp, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

tidy(comp_fit1) %>% 
    gt()
